---
title: "Class_Presentation"
author: "Srikrishna Krishnarao Srinivasan"
date: "January 22, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(gridExtra)
library(knitr)
library(openxlsx)
```

## R Markdown

Analysis of Baldrige Evaluation Criteria and Results for the Cateogry 5.Workforce Focus

#1. The number of items in Workforce Focus category by year

```{r,echo=FALSE}

df=data.frame('year'=1990, 'items_count' = 5)
df=rbind(df, c(1991,5), c(1992,5), c(1993,5), c(1994,5), c(1995,4), c(1996,4), c(1997,3),c(1998,3),c(1999,3),c(2000,3),c(2001,3),c(2002,3),c(2003,3),c(2004,3))
#print(df)

# df1=data.frame('year'=1990, 'items_count' = '5', stringsAsFactors = FALSE)
# df1=rbind(df1, c(1991,'5'), c(1992,'5'), c(1993,'5'), c(1994,'5'), c(1995,'4'), c(1996,'4'))
# print(df1)


p = ggplot(data = df, aes(x=year, y=items_count, fill=year)) +
  geom_bar(stat='identity') +
  geom_text(aes(label=items_count), vjust=1.6, color='white', size=3.5) +
  theme_minimal()

print(p)


#print(df1)

SummaryTable=data.frame('Number'=1,
                        '1990'= 'Human Resource Management', 
                        '1995'='Human Resource Planning and Evaluation',
                        '1997'='Work Systems',
                        '2003'='Work Systems',
                        stringsAsFactors = FALSE)
SummaryTable=rbind(SummaryTable, 
                   c(2,'Employee Involvement', 
                       'High performance work systems', 
                       'Employee Education, Training and Development', 
                       'Employee Learning and Motivation'),
                   c(3,'Quality Education and Training', 
                       'Employee Education Training and Development', 
                       'Employee Well Being and Satisfaction', 
                       'Employee Well Being and Satisfaction'),
                   c(4,'Employee Recognition and Performance Measurement', 
                       'Employee Well being and Satisfaction', 
                       'dropped',
                       'dropped'),
                   c(5,'Employee Well-being and morale',
                       'dropped',
                       'dropped',
                       'dropped'))


kable(SummaryTable)

```

#2. Line chart of average icat5total over years

```{r,echo=FALSE}

setwd('B:/Travel/US/USF_Course/SDM')
df = read.xlsx('baldridge2011-1.xlsx')
#colnames(df)

cat_5_cols = c("i5.1score","i5.1max","i5.2score","i5.2max","i5.3score","i5.3max","i5.4score","i5.4max","i5.5score","i5.5max","i5.6score","i5.6max", "i5.7score", "i5.7max","icat5total","icat5max", 'year', 'sector') 

df = df[, cat_5_cols]
#summary(df)

df_trend = data.frame('year'=1111, 'icat5total_year_avg'=0)

#print(unique(df$year))

for (yr in unique(df$year)) {
  df_yr = df[which(df$year==yr),]
  avg=mean(df_yr$icat5total)
  df_trend = rbind(df_trend, c(yr, avg))
}

df_trend=df_trend[which(df_trend$year>1111),]
# df_yr = df[which(df$year==1991),]
# yr=1991
# avg=mean(df_yr$icat5total)
# df_trend = rbind(df_trend, c(yr, avg))

#print(df_trend)

p1=ggplot(data = df_trend, aes(x=year, y=icat5total_year_avg)) +
  geom_line(color='blue')+
  geom_point() +
  geom_vline(xintercept = 1997, color='red')

print(p1)
  

```

#3. Line chart of average icat5max over years


```{r,echo=FALSE}

df_trend_max = data.frame('year'=1111, 'icat5total_year_max'=0)

#print(unique(df$year))

for (yr in unique(df$year)) {
  df_yr = df[which(df$year==yr),]
  max=max(df_yr$icat5max)
  df_trend_max = rbind(df_trend_max, c(yr, max))
}

df_trend_max=df_trend_max[which(df_trend_max$year>1111),]
# df_yr = df[which(df$year==1991),]
# yr=1991
# avg=mean(df_yr$icat5total)
# df_trend = rbind(df_trend, c(yr, avg))

#print(df_trend)

p2=ggplot(data = df_trend_max, aes(x=year, y=icat5total_year_max)) +
  geom_line(color='blue')+
  geom_point() +
  geom_vline(xintercept = 1997, color='red')

print(p2)
  

```

#4. Hypothesis: The Scoring for Category 5 Workforce Focus was easier after 1997 as the number of items reduced. To verify this, a simple linear regression between the two terms should say if there is significant p-value or not 

```{r,echo=FALSE}


df$year_before_1997 = ifelse(df$year<=1997, 1,0)
df$year_before_1997 = factor(df$year_before_1997)
#summary(df)

regression_model = lm(icat5total ~ year_before_1997, df)
summary(regression_model)

regression_model_1 = lm(icat5total ~ year_before_1997 + I(icat5total-icat5max), df)
summary(regression_model_1)

```


```{r,echo=FALSE}

#http://www.sthda.com/english/wiki/ggplot2-line-plot-quick-start-guide-r-software-and-data-visualization

```
